Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-05 paper/paper.tex
Remove a redundant mention of memory in Markov process

% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.

@@

Rational probabilistic planning can be reformulated
as a standard memory Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what partially observable MDPs do ~\citep{starkweather2017dopamine,o2006making}.

>>>>

@@

% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can thus be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what partially observable MDPs do ~\citep{starkweather2017dopamine,o2006making}.
